\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-24 draft.tex
Typos in 4.3

\newcommand{\todo}[1]{{\color{blue}TODO:#1}}
\newcommand{\hide}[1]{}
\newcommand{\defn}{\overset{\triangle}{=}}
\newcommand{\maxi}{m}
\newcommand{\cur}{cur()}
\newcommand{\dom}[1]{\mathsf{dom}(#1)}
\newcommand{\ite}[3]{
	 \ifmmode
	 \mathbf{if}\ #1 \ \mathbf{then}\ #2\  \mathbf{else}\ #3
	 \else
	 \textbf{if}\ #1 \ \textbf{then}\ #2\  \textbf{else}\ #3
	 \fi}
\newcommand{\rloop}{
	\ifmmode
	\mathbf{Loop}
	\else
	\textbf{Loop}
	\fi}

@@

The MapReduce framework for data-parallel computation was first proposed by
Google~\cite{dean04} and later implemented in the Apache Hadoop
project~\cite{hadoop}. Under the MapReduce framework, a reducer computes output
values from a sequence of input values transmitted over the network. Due to
non-determinism in data transmission, the order in which input values arrive at
the reducer is not fixed. In relation to this, the \emph{commutativity problem}
of reducers asks if the output of a reducer is independent of the order of its
inputs. Indeed, there are several advantages for a reducer to be commutative,
e.g., the verification problem of a MapReduce program can be reduced to the
problem of verifying a sequential program. We present the tool J-ReCoVer (Java
Reducer Commutativity Verifier) that implements effective heuristics for reducer
commutativity analysis. J-ReCoVer is the first tool that is specialized in
checking reducer commutativity. Our experimental results over 118 benchmark
examples collected from open repositories are very positive; J-ReCoVer correctly
handles over 97~\% of them.

@@

MapReduce belongs among the most popular frameworks for data parallel
computation. A MapReduce program~\cite{dean04,hadoop} consists of several pairs
of \emph{mappers} and \emph{reducers} running on a machine cluster for handling
big data in parallel. Usually, mappers and reducers are the only components in a
MapReduce program that involve concurrency. Mappers read data from a distributed
database and output a sequence of \emph{key-value} pairs. The elements of the
sequence (i.e., key-value pairs) with the same key are sent to the same reducer
for further processing. Due to scheduling policies and network latency, the same
inputs may arrive at a reducer in different orders in different executions.
Therefore, reducers are typically required to be \emph{commutative}, that is,
the output of a reducer is required to be independent of the order of its
inputs. The problem of checking whether this is indeed the case is known as the
\emph{commutativity problem} of
reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}. If all reducers
are commutative, they will have the same external behavior under all possible
schedules. In such a case, by fixing a schedule, the verification problem of a
MapReduce program can be reduced to the verification problem of a sequential
program, which is known to be much easier than the verification problem of
concurrent programs. One then suffices with considering any chosen interleaving
of input values instead of all of them.

@@

%=============================================================================
\subsection*{Related Works}
%=============================================================================

The reducer commutativity problem can be reduced to a \emph{program equivalence}
problem. One creates another program $R'$ that first non-deterministically swaps
two consecutive input values and then executes the code of $R$. If $R'$ and $R$
are equivalent, using the fact that all permutations of a list can be obtained
by swapping consecutive list elements finitely many times\footnote{Here is an
example to produce [3;2;5;1;4] from [1;2;3;4;5] by swapping consecutive
elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$
[2;\textbf{1};\textbf{3};4;5] $\rightarrow$
[2;3;1;\textbf{4};\textbf{5}]$\rightarrow$
[2;3;\textbf{1};\textbf{5};4]$\rightarrow$
[\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to
be commutative. There is a series of research results on program equivalence
checking (or closely related topics such as regression verification and
translation validation): see, e.g.,
\cite{Pnueli:1998:TV,fedyukovich2015automated,barthe2011relational,KlebanovRuemmerUlbrich2017}
to name a few.

@@

The input of J-ReCoVer is a reducer program written in Java, which is the most
popular programming language used in the Hadoop~\cite{hadoop} MapReduce
framework. The J-ReCoVer tool has three main components, the
\emph{Preprocessor}, the \emph{Prover}, and the \emph{BugFinder}. As the name
suggests, the Preprocessor reads as input a reducer program and performs the
required preprocessing. The goal of Prover is to show that a given reducer is
commutative, and the goal of BugFinder is the opposite. The architecture of
J-ReCoVer can be found in Figure~\ref{fig:overview-jrecover}. The user can input
a reducer program to J-ReCoVer either through our web-interface or use a binary
application installed on his/her own machine.

@@

		\end{tikzpicture}
	}
		\vspace{-1cm}
	\caption{Overview of the J-ReCoVer Tool. }\label{fig:overview-jrecover}
		\vspace{-0.8cm}

@@

In general, the problem with the input before the loop can be handled as follows,
including the case where $\cur$ occurs multiple times in $s_1$. Assume that the
$s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ has the form
$$s'_0;x_{i_1}{:=} \cur;s'_1; \ldots; x_{i_{m}}{:=}\cur;s'_m$$ where $\cur$ does
not occur in $s'_0,s'_1,\ldots, s'_m$. For all $j \in [1,m]$, we replace the
code $x_{i_j} := \cur; s'_j;$ from $s_1$ by a branch statement with the guard
$s=j$ and body $x_{i_j} := \cur; s'_j; s:=s+1$ in $s_2$. The original $s_2$ loop
body becomes the else branch of the newly introduced guard statement.

@@

We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative. For instance, consider a simple example. In the loop body, the input is first stored in a variable $t$ and then added to $s$. After the loop, output the value of $s$.
In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of the loop body. Observe that
$F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t)) = (c_1+c_2, c_2)$. It follows that the corresponding Equation~(\ref{eq:commu}) is invalid. The second component of the returned tuples corresponds to the value of $t$ after executing the loop body twice. Their values are $c_1$ and $c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$. However, in this case, the value of $t$ will not affect the output of this reducer.

%\begin{figure}[hbt]
%	\begin{minipage}{0.4\textwidth}
%		\begin{algorithm}[H]
%			$s:= 0$; \;
%			\Loop{}{
%				$t:=\cur$;
%				$s:= s + t$\;
%			};
%			$out(s)$\;\;\;
%		\end{algorithm}
%		\caption{A commutative reducer with an invalid 
%                   Equation~(\ref{eq:commu}).}
%		\label{fig:reducer_opt}
%	\end{minipage}
%	\ \ \ \ \ \ \ \
%	\begin{minipage}{0.5\textwidth}
%		\LinesNumbered
%		\centering
%		\begin{minipage}{0.75\textwidth}
%		\begin{algorithm}[H]
%			$c_1;c_2;\ldots;c_i$\;
%			\lIf{$g_1$}{$\ldots$}
%			\lElseIf{ $g_2$}{$\ldots$}
%			\lElseIf{ $g_3$}{$\ldots$}
%			\lElseIf{ $g_m$}{$c_{i+1};\ldots ;c_n; out(v);\ldots$}
%			\lElse{ $\ldots$}
%		\end{algorithm}
%	\end{minipage}
%		\caption{The $s_3$ command with an $out(v)$ command in 
%                   nested branches.}
%		\label{fig:nested_out}
%	\end{minipage}
%\end{figure}

% To handle such a situation, we need an algorithm to collect a set of variables
% whose value may affect the output.  Recall that the first program
% transformation task uses a set of variables $V_2=\{v_{out_k} \mid k \in
% [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$, to
% collect output values occurred in the loop body $s_2$.  The set $V_2$ is
% exactly the set of variables that will affect the output inside the loop.

We perform a simple backward live variable analysis to collect all variables whose value may propagate to the output command after the loop execution. Only these varaibles are required to be equivalent. In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$. The details of the evaluation can be found in Section~\ref{section:exp}.

@@

\paragraph*{Results} J-ReCoVer successfully handled $115$ cases ($97.4\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool. Another $27\%$ of the execution time is in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations. The time spent in Solver is quite limited ($<1\%$), since the real-world integer reducer programs are usually not that big.

>>>>

\newcommand{\todo}[1]{{\color{blue}TODO:#1}}
\newcommand{\hide}[1]{}
\newcommand{\defn}{\overset{\triangle}{=}}
\newcommand{\maxi}{m}
\newcommand{\cur}{cur()}
\newcommand{\dom}[1]{\mathsf{dom}(#1)}
\newcommand{\IF}[2]{
	\ifmmode
	\mathbf{if}\ #1 \ \mathbf{then}\ #2
	\else
	\textbf{if}\ #1 \ \textbf{then}\ #2
	\fi}
\newcommand{\ite}[3]{
	 \ifmmode
	 \mathbf{if}\ #1 \ \mathbf{then}\ #2\  \mathbf{else}\ #3
	 \else
	 \textbf{if}\ #1 \ \textbf{then}\ #2\  \textbf{else}\ #3
	 \fi}
\newcommand{\rloop}{
	\ifmmode
	\mathbf{Loop}
	\else
	\textbf{Loop}
	\fi}

@@

The MapReduce framework for data-parallel computation was first proposed by
Google~\cite{dean04} and later implemented in the Apache Hadoop
project. Under the MapReduce framework, a reducer computes output
values from a sequence of input values transmitted over the network. Due to
non-determinism in data transmission, the order in which input values arrive at
the reducer is not fixed. In relation to this, the \emph{commutativity problem}
of reducers asks if the output of a reducer is independent of the order of its
inputs. Indeed, there are several advantages for a reducer to be commutative,
e.g., the verification problem of a MapReduce program can be reduced to the
problem of verifying a sequential program. We present the tool J-ReCoVer (Java
Reducer Commutativity Verifier) that implements effective heuristics for reducer
commutativity analysis. J-ReCoVer is the first tool that is specialized in
checking reducer commutativity. Our experimental results over 118 benchmark
examples collected from open repositories are very positive; J-ReCoVer correctly
handles over 97~\% of them.

@@

MapReduce belongs among the most popular frameworks for data parallel
computation. A MapReduce program~\cite{dean04} consists of several pairs
of \emph{mappers} and \emph{reducers} running on a machine cluster for handling
big data in parallel. Usually, mappers and reducers are the only components in a
MapReduce program that involve concurrency. Mappers read data from a distributed
database and output a sequence of \emph{key-value} pairs. The elements of the
sequence (i.e., key-value pairs) with the same key are sent to the same reducer
for further processing. Due to scheduling policies and network latency, the same
inputs may arrive at a reducer in different orders in different executions.
Therefore, reducers are typically required to be \emph{commutative}, that is,
the output of a reducer is required to be independent of the order of its
inputs. The problem of checking whether this is indeed the case is known as the
\emph{commutativity problem} of
reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}. If all reducers
are commutative, they will have the same external behavior under all possible
schedules. In such a case, by fixing a schedule, the verification problem of a
MapReduce program can be reduced to the verification problem of a sequential
program, which is known to be much easier than the verification problem of
concurrent programs. One then suffices with considering any chosen interleaving
of input values instead of all of them.

@@

%=============================================================================
\paragraph*{Related Works}
%=============================================================================

The reducer commutativity problem can be reduced to a \emph{program equivalence}
problem. One creates another program $R'$ that first non-deterministically swaps
two consecutive input values and then executes the code of $R$. If $R'$ and $R$
are equivalent, using the fact that all permutations of a list can be obtained
by swapping consecutive list elements finitely many times\footnote{Here is an
example to produce [3;2;5;1;4] from [1;2;3;4;5] by swapping consecutive
elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$
[2;\textbf{1};\textbf{3};4;5] $\rightarrow$
[2;3;1;\textbf{4};\textbf{5}]$\rightarrow$
[2;3;\textbf{1};\textbf{5};4]$\rightarrow$
[\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to
be commutative. There is a series of research results on program equivalence
checking (or closely related topics such as regression verification and
translation validation): c.f.,
\cite{Pnueli:1998:TV,fedyukovich2015automated,barthe2011relational,KlebanovRuemmerUlbrich2017}
to name a few.

@@

The input of J-ReCoVer is a reducer program written in Java, which is the most
popular programming language used in the Hadoop MapReduce
framework. The J-ReCoVer tool has three main components, the
\emph{Preprocessor}, the \emph{Prover}, and the \emph{BugFinder}. As the name
suggests, the Preprocessor reads as input a reducer program and performs the
required preprocessing. The goal of Prover is to show that a given reducer is
commutative, and the goal of BugFinder is the opposite. The architecture of
J-ReCoVer can be found in Figure~\ref{fig:overview-jrecover}. The user can input
a reducer program to J-ReCoVer either through our web-interface or use a binary
application installed on his/her own machine.

@@

		\end{tikzpicture}
	}
		\vspace{-1cm}
	\caption{Overview of the J-ReCoVer tool. }\label{fig:overview-jrecover}
		\vspace{-0.8cm}

@@

In general, the problem with the input before the loop can be handled as follows,
including the case where $\cur$ occurs multiple times in $s_1$. Assume that the
$s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ has the form
$c_0;x_{1}{:=} \cur;c_1; \ldots; x_{m}{:=}\cur;c_m$, where $\cur$ does
not occur in $c_0,c_1,\ldots, c_m$. 
In the transformed reducer, the part before the loop is now $c_0;s:=1$. The loop body contains several branch statements. 
For all $j \in [1,m]$, we add a branch statement $\IF{s=j}{x_{j}:=\cur; c_j; s:=s+1}$. 
We also add $\IF{s=m+1}{s_2}$ for the original loop body.

@@

We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative. For instance, consider a simple example. In the loop body, the input is first stored in a variable $t$ and then added to $s$. 
That is $t:=\cur;s:=t$.
After the loop, output the value of $s$.
In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of the loop body. Observe that
$F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t)) = (c_1+c_2, c_2)$. It follows that the corresponding Equation~(\ref{eq:commu}) is invalid. The second component of the returned tuples corresponds to the value of $t$ after executing the loop body twice. Their values are $c_1$ and $c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$. However, in this case, the value of $t$ will not affect the output of this reducer.
To handle this issue, we perform a simple backward live variable analysis to collect all variables whose value may propagate to the output command after the loop execution. Only these variables are required to be equivalent. In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$ with the help of this optimization.

@@

\paragraph*{Results} J-ReCoVer successfully handled $115$ cases ($97.5\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool. Another $27\%$ of the execution time is in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations. The time spent in Solver is quite limited ($<1\%$), since the real-world integer reducer programs are usually not that big.
